---
title: "Week 02: COVID Visualization Activity"
date: "September, 11 2023"
author: "**`[[`**Jiabin Zheng**`]]`**"
---

Today, we'll be working with a data set related to COVID.
This data is based on data from the the [COVID Tracking Project](https://covidtracking.com/).
I cleaned up this data and also added total populations from the 2020 for each of the relevant categories.
Note, due to differences in the way race and ethnicity are encoded in the census as compared to the the COVID Tracking Project, the population counts for LatinX may be somewhat inaccurate.

```{r load_data}
library(tidyverse)
load("CRDT Data.RData")
ls()
```

I've include 4 different data sets.
They all have the same data but have it represented in different ways.
Try using the different data sets and see which ones are good for making which plots.


```{r first_plot}
ggplot(covid_data_count, aes(x = date, y = Cases)) + geom_point()
```



If you want to only look at a specific state, you can do it like this.
For now, see what you can do just using `ggplot`.

```{r}
covid_data_count |> 
  filter(state == "MA") |> 
  ggplot(aes(x = date, y = Cases, color = race)) + geom_line()
```

1. Write code for a plot and describe what you observe?
```{r}
library(ggplot2)
  covid_data_race |>
  filter(state=="NY") |>
  ggplot(aes(x = date,y = Cases, color = race)) + geom_line()
```
I made a line plot by using "covid_date_race" data set,It describes how many new crown cases, deaths, and hosp there are among whites over time. The case line has a large slope, and the line for deaths and hosp is almost close to zero compared to the case line.
2. Are there any conclusions you can draw?
The difference between the number of deaths and hosp and the number of cases has been increasing over time. As a result, there is an exponential increase in the number of cases, but a relatively small increase in the number of deaths and hosp.
3. What were you not able to do due to not having the R knowledge?
I am not able to compare diff race count with others in one plot.
4. What other data would be useful to better understand this data?
"covid_data_orig" is useful for displaying cases, deaths and hosp in white.
